Functional oxide layers for electrical isolation and chemical passivation of steel substrates

### 2022-08-08 Thesis/chapter/03-theoretical-background.tex
stat

DOEs: randomization, latin square, orthogonal experiment design, full/2-lvl factorial design, placket burman, 
\url{https://www.jstor.org/stable/2238570}\cite{karlin1966optimal}
\url{https://rss.onlinelibrary.wiley.com/doi/abs/10.1111/j.2517-6161.1973.tb00944.x}\cite{whittle1973some}
maybe \url{https://www.sciencedirect.com/science/article/pii/S0167715212003343?via\%3Dihub}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsubsection{Analysis of Variance} % ANOVA
The statistical significance of the experiment is determined by a ratio of two variances. This ratio is independent of several possible alterations to the experimental observations: Adding a constant to all observations does not alter significance. Multiplying all observations by a constant does not alter significance. 
So ANOVA statistical significance result is independent of constant bias and scaling errors as well as the units used in expressing observations. %https://en.wikipedia.org/wiki/Analysis_of_variance#Summary_of_assumptions
\td{make analysis with EMMA dataset and EMMA+DOE}

>>>>

DOEs: randomization, latin square, orthogonal experiment design, full/2-lvl factorial design, placket burman, 
\url{https://www.jstor.org/stable/2238570}\cite{karlin1966optimal}
\url{https://rss.onlinelibrary.wiley.com/doi/abs/10.1111/j.2517-6161.1973.tb00944.x}\cite{whittle1973some}
maybe \url{https://www.sciencedirect.com/science/article/pii/S0167715212003343?via\%3Dihub}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsubsection{Analysis of Variance} % ANOVA
The statistical significance of the experiment is determined by a ratio of two variances. This ratio is independent of several possible alterations to the experimental observations: Adding a constant to all observations does not alter significance. Multiplying all observations by a constant does not alter significance. 
So ANOVA statistical significance result is independent of constant bias and scaling errors as well as the units used in expressing observations. %https://en.wikipedia.org/wiki/Analysis_of_variance#Summary_of_assumptions
\td{make analysis with EMMA dataset and EMMA+DOE}
\url{https://www.scribbr.com/statistics/anova-in-r/} just make input categorical
\url{https://pypi.org/project/pynova/}
\textbf{Assumptions of ANOVA}
from \url{https://statsandr.com/blog/anova-in-r/}
\begin{itemize}
    \item variable type: continuous dependent variable and categorial qualitative independent variable (also called treatments or levels). The input variables are discretized an can therefore be seen as categorial.
    \item Independence: groups and levels should be independent
    \item Normality: the residual (that is the durchschnittliche dependance of uncontrollable variables ,like room temperature or humidity) should approximately follow a normal distribution. 
    \item Equality of variance: variance in differenct groups should be equal (compare with homoscedasticity).
    \item No outliers
\end{itemize}

\textbf{Other statistics}
\begin{itemize}
    \item f-test 
    \item p-value 
    \item t-test
\end{itemize}
